---
title: "Shiny App Presentation"
author: "Ananda Rivas"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

## Introduction  
Welcome to my **Shiny App**! 

🔹 This app lets users **explore datasets interactively**  
🔹 Built with **Shiny & R**  

### **Datasets Available:**  
Users can **select** from three datasets:

* **Iris** 🌸 *(Flower dataset)*  
* **Mtcars** 🚗 *(Car attributes dataset)*  
* **ToothGrowth** 🦷 *(Dental growth dataset)*  

After selection, the app shows dataset details automatically.

## Visualization Options
Users can choose between:

* Scatter Plot

* Box Plot

* Summary Statistics

```{r}
# Mostrar opciones de visualización
plot_types <- c("Scatter Plot", "Box Plot", "Summary Statistics")
plot_types
```
## Interactive Features
Users can:

- Select a dataset

- Choose variables for X and Y axes

- Pick a visualization type

### Example: ToothGrowth Boxplot

```{r,eval=FALSE}
library(ggplot2)
ggplot(ToothGrowth, aes(x = factor(dose), y = len)) + 
  geom_boxplot(color = "#4C9CCF", fill = "#A3C8F0", notch = TRUE) + 
  theme_minimal() +
  labs(title = "Tooth Growth by Dose", x = "Dose", y = "Tooth Length")
```
## 
```{r,echo=FALSE,warning=FALSE,fig.height=3,fig.width=3,fig.align='center'}
library(ggplot2)
ggplot(ToothGrowth, aes(x = factor(dose), y = len)) + 
  geom_boxplot(color = "#4C9CCF", fill = "#A3C8F0", notch = TRUE) + 
  theme_minimal() +
  labs(title = "Tooth Growth by Dose", x = "Dose", y = "Tooth Length")
```

**Conclusion**

* This Shiny app makes data exploration easy!

* Users can analyze & visualize datasets dynamically.

* Try it now! 